### 2023-06-15 about/vita.tex
senang diri

\starleftright{\bf After school care supervisor}{\bf January 2023 -- present}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervise and facilitate activities (e.g., arts and crafts, soccer, board games, drawing/colouring) for children
in grades 1 through 6.
\medbreak

\starleftright{\bf Software developer}{\bf January 2023 -- present}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Develop firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

@@

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Meet with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Hold office hours twice a week and responsible for grading of assignments.
\medbreak

\leftright{\bf First responder}{\bf October 2017 -- September 2021}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2020.
\medbreak

@@

\starleftright{\bf Helpdesk tutor}{\bf September 2018 -- April 2021}
\leftright{\sl Computer Science Undergraduate Society Helpdesk}{\sl Montr\'eal, QC, Canada}
\smallskip
Hold twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered include elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medbreak

@@

\begingroup\frenchspacing
\fictioncount=2
\pubbegin F
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

>>>>

\starleftright{\bf After school care supervisor}{\bf January -- June 2023}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervised and facilitated activities (e.g., arts and crafts, soccer, board games, drawing/colouring, movie
days) for children in grades 1 through 6.
\medbreak

\starleftright{\bf Software developer}{\bf January -- May 2023}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Developed firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

@@

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Held office hours twice a week and responsible for grading of assignments.
\medbreak

\leftright{\bf First responder}{\bf October 2017 -- September 2021}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attended team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2020.
\medbreak

@@

\starleftright{\bf Helpdesk tutor}{\bf September 2018 -- April 2021}
\leftright{\sl Computer Science Undergraduate Society Helpdesk}{\sl Montr\'eal, QC, Canada}
\smallskip
Held twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered included elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medbreak

@@

\begingroup\frenchspacing
\fictioncount=3
\pubbegin F
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing
